\section{Programma}
	The course covers a series of topics from two different branches: security and formal methods. 

	Under security we understand a variety of applied concepts related to the security of multi-user, complex systems where information has varying degrees of confidentiality.
	
	Under formal methods we understand a variety of techniques that make it possible to encode properties such as security, performance, etc. of complex systems into programming languages or similar constructs. This allows users to easily find violation of such properties reliably and without testing through advanced compilers.
	
	\subsection*{Security topics}

	For the security part:
	\begin{itemize}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  Cryptography
	\end{itemize}

	\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  history and applications
	\item
	  symmetric cryptography
	\item
	  asymmetric cryptography
	\item
	  key management
	\item
	  implementation issues
	\end{enumerate}

	\begin{itemize}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  Computer security
	\end{itemize}

	\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  principles of system security
	\item
	  access control and authentication
	\item
	  auditing and forensics
	\item
	  secure coding and hardening
	\item
	  reversing and exploitation
	\end{enumerate}

	\begin{itemize}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  Network security
	\end{itemize}

	\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  channels, layers, and protocols
	\item
	  architectures and perimeters
	\item
	  common networked applications
	\item
	  building distributed systems
	\item
	  prevention, detection, and response
	\end{enumerate}

	\begin{itemize}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  Humanoid security
	\end{itemize}

	\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\itemsep1pt\parskip0pt\parsep0pt
	\item
	  security management
	\item
	  social engineering and usability
	\item
	  computer crime and economics
	\item
	  international relations / security studies
	\item
	  trust, evaluation, and assurance
	\end{enumerate}

	\subsection*{Formal methods topics}
		The minor mainly focuses on the implementation of formal methods with a meta-compiler, provided by the lecturers. This meta-compiler is accompanied by sample implementations of programming languages, of varying degrees of complexity.
		
		The meta-compiler itself is a formal system, built in the F\# programming language. This means that as an additional level of complexity it is possible for students to add highly abstract properties to the meta-compiler instead of using it to implement languages with these properties.
